---
title: "Results - area per area for areas with only oceanic habitat"
author: "Lola Gilbert"
date: "31/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# California current

Survey area only covered oceanic habitats here, so we just look at the contribution of taxa. 

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_Calif)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_Calif), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_Calif), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

# Gulf of Mexico
Survey area only included oceanic habitat here, so we just look at the contributions of taxa. 

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_GoMex)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_GoMex), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_GoMex), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

# New Caledonia

Survey area only included oceanic habitat here, so we just look at the contributions of taxa. 

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_NCal)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_NCal), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_NCal), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


# Hawaii

Survey area only included oceanic habitat here, so we just look at the contributions of taxa. 

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_Haw)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_Haw), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_Haw), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


# Wallis & Futuna

Survey area only included oceanic habitat here, so we just look at the contributions of taxa. 

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_WFu)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_WFu), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_WFu), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


# French Polynesia

Survey area only included oceanic habitat here, so we just look at the contributions of taxa. 

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_FPol)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_FPol), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_FPol), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```
