---
title: "Results - area per area for areas with both neritic and oceanic habitats"
author: "Lola Gilbert"
date: "31/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Northeast Atlantic

## Excretion in neritic and oceanic waters

In absolute value, is there more excretion in an habitat than in the other ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_abs_NEA_output)
```
 
The full results being: 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_tns_yr_NEA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

And per unit area, so considering the respective size of each of the habitat ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_km2_NEA_output)
```

The details being: 


```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_kg_km2_yr_NEA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


Are the differences between the two areas significant ? (per surface unit)

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_hab_NEA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_NEA_output)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_NEA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_NEA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa and per habitat

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_taxa_NEA_output)
```

Are the differences significant ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_hab_NEA), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What is the relative contribution to total excretion in each habitat ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_hab_NEA), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


# Central North Atlantic

## Excretion in neritic and oceanic waters

In absolute value, is there more excretion in an habitat than in the other ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_abs_CNA_output)
```
 
The full results being: 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_tns_yr_CNA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

And per unit area, so considering the respective size of each of the habitat ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_km2_CNA_output)
```

The details being: 


```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_kg_km2_yr_CNA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


Are the differences between the two areas significant ? (per surface unit)

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_hab_CNA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_CNA_output)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_CNA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_CNA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa and per habitat

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_taxa_CNA_output)
```

Are the differences significant ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_hab_CNA), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What is the relative contribution to total excretion in each habitat ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_hab_CNA), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


# Gulf of Alaska

## Excretion in neritic and oceanic waters

In absolute value, is there more excretion in an habitat than in the other ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_abs_GoAl_output)
```
 
The full results being: 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_tns_yr_GoAl_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

And per unit area, so considering the respective size of each of the habitat ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_km2_GoAl_output)
```

The details being: 


```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_kg_km2_yr_GoAl_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


Are the differences between the two areas significant ? (per surface unit)

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_hab_GoAl_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_GoAl_output)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_GoAl_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_GoAl_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa and per habitat

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_taxa_GoAl_output)
```

Are the differences significant ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_hab_GoAl), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What is the relative contribution to total excretion in each habitat ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_hab_GoAl), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

# Northwest Atlantic 

## Excretion in neritic and oceanic waters

In absolute value, is there more excretion in an habitat than in the other ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_abs_NWA_output)
```
 
The full results being: 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_tns_yr_NWA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

And per unit area, so considering the respective size of each of the habitat ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_km2_NWA_output)
```

The details being: 


```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_kg_km2_yr_NWA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


Are the differences between the two areas significant ? (per surface unit)

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_hab_NWA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_NWA_output)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_NWA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_NWA_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa and per habitat

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_taxa_NWA_output)
```

Are the differences significant ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_hab_NWA), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What is the relative contribution to total excretion in each habitat ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_hab_NWA), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


# Mediterranean Sea

## Excretion in neritic and oceanic waters

In absolute value, is there more excretion in an habitat than in the other ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_abs_Med_output)
```
 
The full results being: 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_tns_yr_Med_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

And per unit area, so considering the respective size of each of the habitat ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_km2_Med_output)
```

The details being: 


```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_kg_km2_yr_Med_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


Are the differences between the two areas significant ? (per surface unit)

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_hab_Med_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_Med_output)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_Med_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are there relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_Med_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa and per habitat

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_taxa_Med_output)
```

Are the differences significant ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_hab_Med), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What is the relative contribution to total excretion in each habitat ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_hab_Med), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


# West Indian Ocean 

## Excretion in neritic and oceanic waters

In absolute value, is there more excretion in an habitat than in the other ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_abs_WIO_output)
```
 
The full results being: 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_tns_yr_WIO_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

And per unit area, so considering the respective size of each of the habitat ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_km2_WIO_output)
```

The details being: 


```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_kg_km2_yr_WIO_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


Are the differences between the two areas significant ? (per surface unit)

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_hab_WIO_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_WIO_output)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_WIO_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are their relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_WIO_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa and per habitat

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_taxa_WIO_output)
```

Are the differences significant ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_hab_WIO), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What is the relative contribution to total excretion in each habitat ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_hab_WIO), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

# French Antilles

## Excretion in neritic and oceanic waters

In absolute value, is there more excretion in an habitat than in the other ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_abs_Ant_output)
```
 
The full results being: 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_tns_yr_Ant_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

And per unit area, so considering the respective size of each of the habitat ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_km2_Ant_output)
```

The details being: 


```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_kg_km2_yr_Ant_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


Are the differences between the two areas significant ? (per surface unit)

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_hab_Ant_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_Ant_output)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_Ant_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are their relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_Ant), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa and per habitat

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_taxa_Ant_output)
```

Are the differences significant ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_hab_Ant), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What is the relative contribution to total excretion in each habitat ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_hab_Ant), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

# French Guyana

## Excretion in neritic and oceanic waters

In absolute value, is there more excretion in an habitat than in the other ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_abs_Guy_output)
```
 
The full results being: 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_tns_yr_Guy_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

And per unit area, so considering the respective size of each of the habitat ? 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_km2_Guy_output)
```

The details being: 


```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(est_stat_hab_kg_km2_yr_Guy_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


Are the differences between the two areas significant ? (per surface unit)

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_hab_Guy_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_Guy_output)
```

Are the differences significant ?

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_tot_Guy_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What are their relative contribution to total excretion in this area ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_tot_Guy_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

## Excretion per taxa and per habitat

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_hab_taxa_Guy_output)
```

Are the differences significant ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(test_diff_taxa_hab_Guy), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

What is the relative contribution to total excretion in each habitat ? 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(taxa_contrib_hab_Guy), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```
