---
title: "Figures & Tables for the article"
author: "Lola Gilbert"
date: '2022-06-17'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

This project is available on 
_[github](https://github.com/Lola-san/Cetacean.excretion.global.git)_

# Relative composition of poop 

Table with stat, no normalization : 
```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(tib_poop_compo_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

And with normalization: 

```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(tib_poop_compo_norm_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```

Significance of the differences: 
```{r  echo=FALSE, fig.align="center"}
# to disable scientific notations
options(scipen = 999)

kableExtra::kable(targets::tar_read(tib_test_diff_poop_compo_output), 
                  align = 'c' , 
                  booktabs = TRUE) |>
  kableExtra::kable_styling()
```


Boxplot showing this: 

```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_compo_poop_boxplot_output)
```



# Relative contribution of taxa in each area 

Northeast Atlantic:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_NEA_output)
```

Central North Atlantic:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_CNA_output)
```

Northwest Atlantic:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_NWA_output)
```


Mediterranean sea:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_Med_output)
```


Gulf of Mexico:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_GoMex_output)
```

French Antilles:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_Ant_output)
```

French Guyana:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_Guy_output)
```

Southwest Indian ocean:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_WIO_output)
```

New Caledonia:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_NCal_output)
```

Wallis & Futuna:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_WFu_output)
```

French Polynesia:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_FPol_output)
```

Hawaii:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_Haw_output)
```

Gulf of Alaska:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_GoAl_output)
```

California current:
```{r  echo=FALSE, fig.align="center"}
targets::tar_read(fig_contrib_taxa_stackbar_Calif_output)
```